% Use htlatex [filename] to make an html version that can be dumped into blogger

%%% PREAMBLE %%%


\documentclass[letterpaper]{article}

%%% PACKAGES %%%

\usepackage[T1]{fontenc} % another stupid thing to make latex reasonably up to date
% - Should help to make copy and paste to text more straightforward
% \usepackage[pdftex]{graphicx} % Add graphics capabilities
\usepackage{multicol} % use for two columns. See: http://physical-thought.blogspot.com/2008/09/two-column-layouts-in-latex.html
% \usepackage{setspace}
\pagestyle{empty}
% Suppresses pagenumbers and other things

%%% COMMANDS %%%
\renewcommand{\familydefault}{\sfdefault} % use sans fonts
% \usepackage{microtype} % Pretty sure I don't need this.
% \DisableLigatures{encoding = *, family = * } % supposed to disable ligatures
\usepackage[small,compact]{titlesec} % Don't use the ridiculous latex sized sections
% \usepackage[colorlinks=true,linkcolor=red]{hyperref} % Hyperlink capabilities - supposed to come last

\title{Chinese Finger Trap}
\author{}
\date{\today}
%%% BODY OF THE DOCUMENT: %%%
\begin{document}
\maketitle
% Alternative Title section
%   \noindent
%   \Large{\emph{Chinese Finger Trap}} \\% Title goes here
   % Xmas porn for jula 2015 - _Chinese_ fingercuffs?
%   \normalsize % return font to normal size
%   \textbf{by } | \today \\ % today's date.
%   \vspace{1mm} % add a little vertical whitespace so the HR shows up
%   \hrulefill \\ % Horizontal rule
%\\
% End of Title section
\begin{multicols}{2}
% This story is about a girl who meets a dude at a concert.
% He recognizes her from some previous event, and says hi. She's shy but admits she reconizes him too.
% They flirt casually, for a bit, and then his friend returns from the bathroom. All three hit it off.
% They end up back at the friend's apartment nearby, after the show.
% It turns into a threesome, with her jacking both of them off. And that of course turns into DP, and that turns into fingercuffs.
% Turns out, she's Chinese. The idea of "fingercuffs" is of course never mentioned, other than the title.
% How do you get the topic of chinese to come up? Do they order chinese food? This should be the delicate/subtle part. talking about family? or talking about some celbrity who is half asian but doesn't look it - Brandon Lee? That's nice because she can think something like "you idiot" before gently correcting him. This could have nice tones about millenials and modern generations, without getting specific about that crap. Could related to millenial sexual habits as well. Except that nobody but gen xers would know who brandon lee was.
% told from her perspective? I think so.
% But what's the larger theme? something about how she doesn't want any dudes, but in fact needs two dudes. That she is the "trap". That she needs it in both ends. That they can't get it out once they are in, she holds them there.
% How do I get around names for them? I hate naming characters.  One is hirsute - Hairy? and the other is Tall.
%

``Oh crap. Please don't let him recognize me,'' she thought as she realized the back of the head she was staring at was in fact the same guy she had met at that talk a couple of weeks before.
He had been pleasant enough then, but she hadn't really talked to him, just been introduced by a mutual friend.
And she was shy, she didn't really want to have that conversation where they went through the ritual of mutual recognition and awkward re-acquaintancing. Was that a real word?
She wasn't sure. But she that process was something she liked to avoid in any situation, but she particularly didn't like talking to people at concerts.

Damn. He keeps looking around. As if he is looking for someone he knows at this show.
Damn. He totally looked at her. She was doomed.
Though she only had herself to blame.
She might be shy, but her piercings gave her away in any social situation.
She cursed her younger anti-normalcy self for being so committed to looking the part.
Wait. Maybe he didn't see her. He was looking back towards the stage now.
But\ldots no. He keeps looking back, and every time a little longer in her direction. It was only a matter of time now.

The first act ended. Boy, they really sucked. She tried to remember the last time she had seen an opening act she liked.
Now he's moving towards her.
Maybe he's just going to the bathroom?
No, wrong vector for the bathroom. Shit.
She could just start walking away, right? She had been carefully avoiding his eyes, focusing on the stage, which now had nothing more entertaining than a few heavyset dudes bending over to put down gaffers tape on cables.

He stood in front of her. He said hi.
Well, no avoiding it now. She looked at him.
Actually, he was kinda cute. She liked that he was tall and kinda skinny. 
He was dressed poorly. 
The kind of way a guy who used to dress ``goth'' in his youth might if he had grown up into a semi-respectable person. Mostly in black, but not well considered clothes. Plus a cycling cap? That was a little weird.

``Didn't we meet at that talk a few weeks ago?'' he asked.

Duh. Yes. How often could he possibly meet people who look like me?
But it was inevitable now.
Commence re-acquaintancing. 

She steeled herself and launched into it: ``Yeah. Funny running into you here too. You think that a coincidence like that is a sign that we are meant to be together or something?''

``Uh, that wasn't really what I was thinking. I just thought it would be weird if I didn't say hi. But maybe you're right, maybe it is a sign.''
He looked down at her with kinda dumb wry smile.
What was he so proud of? That wasn't a smart thing to say at all!
``Want to come up front with me? We can push our way forward for a better view.''

``I guess if the gods have willed it that we meet here, I might as well stand next to you during a show where it will be far too loud to have any kind of conversation anyway.''

He took her hand (so ridiculous!) and they inched forward, squeezing sideways through the crowd, trying not to be rude, but it was a rock show. Rudeness is inevitable.
He deftly maneuvered her in front of him, which she admitted made sense since he was a decent amount taller than her.
Of course that did nothing to help her see past all the beanpole hipster dudes standing directly in front of her.

The crowd was starting to get impatient, and packing more tightly towards the stage. He made idle chit chat with her.
Dumb comments about this band, and weak observations about the hipster crowd.
He still occasionally looked around at the crowd behind them, and soon she realized it was because he wasn't here alone, his friend waved to him as he inched his way up to them through the crowd.

His friend was quite a big shorter and a lot less skinny.
Not fat, just kind of ``stocky'' and muscular.
A low center of gravity. She got a distinct feeling that he would be a powerful lover.
Not that she let her thoughts get off too far in that direction.
Maybe it was just his big mountain man beard.
If he were a Dungeons and Dragons character, he'd be a dwarf.

He completely failed to introduce himself or even really acknowledge her presence. God, these two were worse at social interactions than she was herself. Ach!
She realized the tall one's name had slipped her mind too.
She decided in her head she would just refer to them as Tall and Hairy.

The band came on, there wasn't much space, time, or audible conversation to be had anyway.
The show was good. The crowd pushed forward in their excitement.
Tall kept his arm around her. 
Trying to protect her? From what? All the skinny hipster losers?
Still, it was kinda cute, and she had to admit to herself that she liked it when the crowd pressed him up against her.
Somehow Hairy had gotten maneuvered in front of her.
And as the second encore got going, the crowd surged repeatedly, crushing her between these two dudes. It was hot, and sweaty, and it smelled like Prell from all these dudes with long hair and cheap shampoo.

Tall seemed to have a knack for letting the crowd push him against her, and her against Hairy's warm muscular back, but still keeping his arms around her, and protecting her from the worst of the crush. 
His hands occasionally drifted down to her hips, and once or twice slipped under the curve of her ass. 
When he was crushed against her, she could feel his hard on grinding against her ass.
God, he's so vulgar.
She didn't acknowledge it in any way. 
She wanted to let him believe that he got away with feeling her up as just a normal part of seeing the show.

After the show they wandered outside and stood around chatting as the bouncers kept urging the crowd to disperse faster.

Hairy said, ``Are you guys hungry? There's a mediocre Chinese place around the corner. We could pick something 





\end{multicols}
\end{document}
